Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-28 paper/paper-mainfile.tex
Add lin statistics

Unfortunately, when using simple inference, there are very few problems for which all partially ordered methods are linearized without conflict.
Fortunately, when using complex inference, most partially ordered methods in all problems are linearized without conflict.
%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

@@

\begin{table} 
	\centering
	\caption{These results are from using Simple Inference. Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
	\label{table:SimpleLinearizable} 
		\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
		\midrule
Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
Monroe & 12127.3 & 3447.8 & 72.4  \\ 
Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
PCP & 12.3 & 12.3 & 0.0  \\ 
Rover & 509.4 & 355.2 & 32.3  \\ 
Satellite & 70.6 & 36.1 & 50.9  \\ 
SmartPhone & 6.3 & 4.0 & 21.8  \\ 
Transport & 1144.9 & 1144.9 & 0.0  \\ 
UM-Translog & 1.5 & 1.5 & 0.0  \\ 
Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
Zenotravel & 190.2 & 99.4 & 47.0  \\ 
		\bottomrule 
	\end{tabular} 
}
\end{table}

\begin{table} 
	\centering
	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
	\label{table:ComplexLinearizable} 
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
		\midrule
			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
			Monroe & 12127.3 & 216.9 & 98.2  \\ 
			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
			PCP & 12.3 & 4.9 & 59.8  \\ 
			Rover & 509.4 & 134.8 & 72.4  \\ 
			Satellite & 70.6 & 10.7 & 77.9  \\ 
			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
			Transport & 1144.9 & 0.0 & 100.0  \\ 
			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
			Woodworking & 1927.3 & 476.0 & 85.5  \\
			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
			\bottomrule 
		\end{tabular} 
		}
\end{table}

>>>>

Unfortunately, when using simple inference, there are no problems for which all methods are linearized without conflict.
When using complex inference, the number of methods in all problems that are linearized without conflict is generally higher, with a few problems being provably solvable. 
%Figure~\ref{fig:MethodsLinearizedWOCycleBreak} shows the comparison between the two.

@@

\begin{table} 
	\centering  
	\caption{Number of Problems per Domain for Which \emph{all} methods were linearizable, and the Average Number of Methods with more than 1 sub-task that were in that Domain}
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule
		Domain      & Avg. Num. Methods ($>$ 1) & Num. Problems \\
		\midrule
		SmartPhone  & 4.0                   &  1     \\
		Transport   & 1144.9                & 40       \\
		UM-Translog & 1.1                    & 17   \\
		Woodworking & 2035              &   21    \\
				\bottomrule 
	\end{tabular} 
	}
\end{table}

\begin{table} 
	\centering
	\caption{These results are from using Simple Inference. Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
	\label{table:SimpleLinearizable} 
		\scalebox{0.65} { 
	\begin{tabular}{lcccl} 
		\toprule 
		& Avg. Num. Methods ($>$ 1) & Cycle-breaking & Percentage &  \\ 
		\midrule
Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
Monroe & 12127.3 & 3447.8 & 72.4  \\ 
Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
PCP & 12.3 & 12.3 & 0.0  \\ 
Rover & 509.4 & 355.2 & 32.3  \\ 
Satellite & 70.6 & 36.1 & 50.9  \\ 
SmartPhone & 6.3 & 4.0 & 21.8  \\ 
Transport & 1144.9 & 1144.9 & 0.0  \\ 
UM-Translog & 1.5 & 1.5 & 0.0  \\ 
Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
Zenotravel & 190.2 & 99.4 & 47.0  \\ 
		\bottomrule 
	\end{tabular} 
}
\end{table}

\begin{table} 
	\centering
	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
	\label{table:ComplexLinearizable} 
	\scalebox{0.65} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&  Avg. Num. Methods ($>$ 1)& Cycle-breaking & Percentage &  \\ 
		\midrule
			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
			Monroe & 12127.3 & 216.9 & 98.2  \\ 
			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
			PCP & 12.3 & 4.9 & 59.8  \\ 
			Rover & 509.4 & 134.8 & 72.4  \\ 
			Satellite & 70.6 & 10.7 & 77.9  \\ 
			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
			Transport & 1144.9 & 0.0 & 100.0  \\ 
			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
			Woodworking & 1927.3 & 476.0 & 85.5  \\
			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
			\bottomrule 
		\end{tabular} 
		}
\end{table}
